---
title: Lab Thirteen -- Statistical Inference # Title of the document

# Bibliography Details
bibliography: Lab13References.bib  # Name of bib file in the same folder 
bibliographystyle: apa            # Bibliography style

execute:               # Default settings for code blocks
  warning: false       # Do not print warnings
  message: false       # Do not print messages
  size: "scriptsize"   # Set code size to script size

# Below will do html by default. To render the entire project
# Use the following code:
# quarto::quarto_render("Lab10WriteUp.qmd")
format:
  pdf:        # Specify .pdf formatting options 
    documentclass: article     # Document Class
    number-sections: true      # Number Sections
    reference-section-title: "References" # Title for reference section
    code-line-numbers: true    # Line numbers printed in code
    cap-location: top          # Captions at the top of tables 
    geometry:
      - top=0.75in
      - left=0.75in
      - bottom=0.75in
      - right=0.75in
  html:       # Specify HTML formatting options 
    number-sections: true      # Number Sections
    code-fold: true            # Button to show code
    code-line-numbers: true    # Line numbers printed in code
    cap-location: top          # Captions at the top of tables and figures
format-links: [pdf]
---

```{r}
#| echo: false

default_chunk_hook  <- knitr::knit_hooks$get("chunk")

latex_font_size <- c("Huge", "huge", "LARGE", "Large", 
                     "large", "normalsize", "small", 
                     "footnotesize", "scriptsize", "tiny")

knitr::knit_hooks$set(chunk = function(x, options) {
  x <- default_chunk_hook(x, options)
  if(options$size %in% latex_font_size) {
    paste0("\n \\", options$size, "\n\n", 
      x, 
      "\n\n \\normalsize"
    )
  } else {
    x
  }
})
```

```{r}
#| label: load-packages
#| include: false
library(tidyverse)
library(patchwork)
library(e1071)
library(effectsize)
```

# Remaining Portfolio Work!

**By 5p 4/27** Email me a link to your GitHub page with all polished labs rendered, and your review material (at least one unit). In the email, you should include a reflection about the processes involved in creating this portfolio and what you learned as a result. If you're having trouble reflecting, consider Fink's Taxonomy of Significant Learning (Google Fink taxonomy aligned self-reflection questions). In the email, let me know whether you would be comfortable sharing your page -- I'm hoping that together we can get a good study guide for the final.

# Statistical Inference

@Kasdin25 show that dopamine in the brains of young zebra finches acts as 
a learning signal, increasing when they sing closer to their adult song and 
decreasing when they sing further away, effectively guiding their vocal 
development through trial-and-error. This suggests that complex natural 
behaviors, like learning to sing, are shaped by dopamine-driven reinforcement 
learning, similar to how artificial intelligence learns. You can find the 
paper at this link: [https://www.nature.com/articles/s41586-025-08729-1](https://www.nature.com/articles/s41586-025-08729-1).

Note that the measurement is rather complicated. First, the measurements are taken on syllables of a bird song. When discussing bird songs, the term syllable refers to a single, distinct, uninterrupted sound that is part of a
possibly complex bird song.

They initially describe their measurement as follows. They compare the sound of the developing zebra finches to the median sound of adult zebra finches, that act as a "goal" sound.
\begin{quote}
"For each syllable rendition, we calculated the proximity (Euclidean distance) to the median of the adult renditions of the syllable (age $>$ 90 days) in feature space (Fig. 2a,b)."
\end{quote}

They contextualize that measurement by computing a "relative quality" that takes into account their current ability (e.g., are they getting closer or further compared to their previous 14 renditions).
\begin{quote}
"Because dopamine is hypothesized to encode the relative value of performance, we defined the 'relative quality' of a syllable as proximity to the adult version of the syllable relative to the mean of the previous 14 renditions (Methods)."
\end{quote}

They define the "closer" measurements as the 10% of syllable renditions with the highest relative quality and the "further" as the lowest 10%.
\begin{quote}
"To test for online error responses, for each day we compared the dopamine activity associated with the 10% of syllable renditions with the highest relative quality with that of the 10% of renditions with the lowest relative quality (Fig. 2c–g)."
\end{quote}

Note that the data are measures of dopamine change, they use fibre photometry, changes in the fluorescence indicate dopamine changes in realtime. Their specific measurement considers the percent change in flourescence in 100-ms windows between 200 and 300 ms from the start of singing, averaged across development.

Finally, the researchers note that they adjust the observations to correct for the increased dopamine for singing at all (whether it is close or far).
\begin{quote}
"As previously reported, the baseline level of dopamine in Area X is known to increase during singing; to isolate the effect of syllable quality from these singing-related dopamine increases, we subtracted the mean dopamine response across all renditions of a syllable on each day from the dopamine response for each rendition."
\end{quote}

So, the random variables we are working with are:
\begin{align*}
X_{\text{close}} &= \text{average \% change in fluorescence for the top 10\% syllable renditions} \\
&\quad \text{relative to distance from adult sound (corrected for singing)} \\[1ex]
X_{\text{far}} &= \text{average \% change in fluorescence for the bottom 10\% syllable renditions} \\
&\quad \text{relative to distance from adult sound (corrected for singing)}
\end{align*}

That is, the unit of measure is the syllable as measured on six birds, and the measurement is somewhat complicated.

## Part a
Using the `pwr` package for \texttt{R} [@pwr], conduct a power analysis. How many observations would the researchers need to detect a moderate-to-large effect ($d=0.65$) when using $\alpha=0.05$ and default power (0.80) for a two-sided one sample $t$ test.

**Solution**

```{r}
library("pwr")
pwr.t.test(d = 0.65, power = 0.80, alternative = "two.sided", type="one.sample")
```

## Part b
Click the link to go to the paper. Find the source data for Figure 2. Download the Excel file. Describe what you needed to do to collect the data for Figure 2(g). Note that you only need the `closer_vals` and `further_vals`. Ensure to `mutate()` the data to get a difference (e.g., `closer_vals - further_vals`).

**Solution**

After finding and downloading the data, I put both the closer_vals and the further_vals on the same table in different columns. I then exported this as a CSV to this lab.

```{r}
dat.kasdin = read.csv("41586_2025_8729_MOESM4_ESM.csv") #reads csv file
dat.kasdin.cleaned = dat.kasdin |>
                        mutate(difference = Closer_vals - Farther_vals)
# saves new table and passes table through the mutate function
# uses mutate function to create new difference column
```

## Part c
Summarize the data.

* Summarize the further data. Do the data suggest that dopamine in the brains of young zebra finches decreases when they sing further away?
* Summarize the closer data. Do the data suggest that dopamine in the brains of young zebra finches increases when they sing closer to their adult song?
* Summarize the paired differences. Do the data suggest that there is a difference between dopamine in the brains of young zebra finches when they sing further away compared to closer to their adult song?
* **Optional Challenge** Can you reproduce Figure 2(g)? Note that the you can use \texttt{geom\_errorbar()} to plot the range created by adding the mean $\pm$ one standard deviation.

**Solution**

```{r}
ggplot(dat.kasdin.cleaned) + # Specify Data
  geom_violin(aes(x = "", # Specify no grouping
      y = Closer_vals), # Specify y-axis
fill = "lightgrey", alpha=0.5) + # A transparent light grey
geom_boxplot(aes(x = "", # Specify no grouping
y = Closer_vals), # Specify y-axis
width = 0.1)+
theme_bw() + # A cleaner theme
labs(x = "", # Specify axis labels
y = "Percent Change in fluorescence") +
ggtitle("Change in fluorescence for the top 10%") + # Plot title
theme(axis.ticks.x = element_blank()) # Remove x-axis tick
```

```{r}
dat.kasdin.cleaned.summary <- dat.kasdin.cleaned |>
  summarize( #calculates data for a table with the following measures
    n = n(),
    Mean = mean(Closer_vals, na.rm = T),
    SD = sd(Closer_vals, na.rm = T),
    Median = median(Closer_vals, na.rm = T),
    IQR = IQR(Closer_vals, na.rm = T),
    Skewness = e1071::skewness(Closer_vals, na.rm = T),
    "Excess Kurtosis" = e1071::kurtosis(Closer_vals, na.rm = T)
  ) 
```

```{r}
#| label: tbl-close
#| tbl-cap: "Fluorescence Percent Changes For Closer"
#| tbl-align: "center"
#| echo: false
dat.kasdin.cleaned.summary |>
  knitr::kable(digits = 3) #digits specify decimal in table values
```

The data does suggest that the dopamine in the brains of young zebra finches increases when they sing closer as both the median and mean show an increase in the percent of dopamine experiences by the finches. While the data distribtion is fairly platykurtic, the majority of the values are increases based on the IQR and standard deviation.

```{r}
ggplot(dat.kasdin.cleaned) + # Specify Data
  geom_violin(aes(x = "", # Specify no grouping
                  y = Farther_vals), # Specify y-axis
                  fill = "lightgrey", alpha=0.5) + # A transparent light grey
  geom_boxplot(aes(x = "", # Specify no grouping
                   y = Farther_vals), # Specify y-axis
                   width = 0.1)+
  theme_bw() + # A cleaner theme
  labs(x = "", # Specify axis labels
       y = "Percent Change in fluorescence") +
ggtitle("Change in fluorescence for the bottom 10%") + # Plot title
theme(axis.ticks.x = element_blank()) # Remove x-axis tick
```

```{r}
dat.kasdin.cleaned.summary <- dat.kasdin.cleaned |>
  summarize( #calculates data for a table with the following measures
    n = n(),
    Mean = mean(Farther_vals, na.rm = T),
    SD = sd(Farther_vals, na.rm = T),
    Median = median(Farther_vals, na.rm = T),
    IQR = IQR(Farther_vals, na.rm = T),
    Skewness = e1071::skewness(Farther_vals, na.rm = T),
    "Excess Kurtosis" = e1071::kurtosis(Farther_vals, na.rm = T)
  ) 
```

```{r}
#| label: tbl-farth
#| tbl-cap: "Fluorescence Percent Changes For Farther"
#| tbl-align: "center"
#| echo: false
dat.kasdin.cleaned.summary |>
  knitr::kable(digits = 3) #digits specify decimal in table values
```

The data does suggest that the dopamine in the brains of young zebra finches decreases when they sing further away as both the median and mean show a decrease in the percent of dopamine experiences by the finches. Because the distribution is fairly skewed, using the IQR, the middle 50% experience a decrease in dopamine. 

```{r}
ggplot(dat.kasdin.cleaned) + # Specify Data
  geom_violin(aes(x = "", # Specify no grouping
                  y = difference), # Specify y-axis
                  fill = "lightgrey", alpha=0.5) + # A transparent light grey
  geom_boxplot(aes(x = "", # Specify no grouping
                   y = difference), # Specify y-axis
                   width = 0.1)+
  theme_bw() + # A cleaner theme
  labs(x = "", # Specify axis labels
       y = "Percent Change in fluorescence") +
ggtitle("Fluorescence difference change between groups") + # Plot title
theme(axis.ticks.x = element_blank()) # Remove x-axis tick
```

```{r}
dat.kasdin.cleaned.summary <- dat.kasdin.cleaned |>
  summarize( #calculates data for a table with the following measures
    n = n(),
    Mean = mean(difference, na.rm = T),
    SD = sd(difference, na.rm = T),
    Median = median(difference, na.rm = T),
    IQR = IQR(difference, na.rm = T),
    Skewness = e1071::skewness(difference, na.rm = T),
    "Excess Kurtosis" = e1071::kurtosis(difference, na.rm = T)
  ) 
```

```{r}
#| label: tbl-diff
#| tbl-cap: "Differences in Fluorescence"
#| tbl-align: "center"
#| echo: false
dat.kasdin.cleaned.summary |>
  knitr::kable(digits = 3) #digits specify decimal in table values
```

These data summaries do suggest that there is a difference between the dopamine levels of the zebra finches singing closer and farther away. The mean and medians both summarize that the difference is not centered at zero, suggesting that there is a difference. Additionally, zero is not contained in the IQR and is over one standard deviation away from the center, demonstrating that no difference is not common in this data.

## Part d
Conduct the inferences they do in the paper. Make sure to report the results a little more comprehensively -- that is your parenthetical should look something like: ($t=23.99$, $p<0.0001$; $g=1.34$; 95% CI: 4.43, 4.60). Ensure to verify any conditions for use.\
**Note**: Your numbers will vary slightly because they reported two-sided test $p$-values instead of the specified one-sided tests. 

**Solution**

*Conditions*

```{r}
#| label: fig-SamplingDistributions
#| fig-cap: "Sampling Distributions."
#| fig-width: 10
#| fig-height: 6
#| scale: "80%"
#| fig-align: "center"

set.seed(3434)

mu0 = 0

 # Resampling
 fts <- rep(NA, 1000) #creates empty vectors
 fs <- sd(dat.kasdin.cleaned$Farther_vals)
 n <- nrow(dat.kasdin.cleaned)
 for(i in 1:1000){
   curr.sample <- sample(dat.kasdin.cleaned$Farther_vals, size=n, replace=T)
   fts[i] <- (mean(curr.sample) - mu0)/(fs/sqrt(n))
 }
 #resample the data of farther values 1000 times and save the means

 p1 <- ggplot() +
   stat_density(data=tibble(t=fts), aes(x=t), color="grey", geom="line")+
   geom_hline(yintercept=0) +
   theme_bw()+
   labs(x=bquote(t),
   y="Density",
   caption=paste("mean:", round(mean(fts),2), ", sd:", round(sd(fs),2)))+
   ggtitle("Farther Values") # Plot title
 

# Resampling
 cts <- rep(NA, 1000)
 cs <- sd(dat.kasdin.cleaned$Closer_vals)
 n <- nrow(dat.kasdin.cleaned)
 for(i in 1:1000){
 curr.sample <- sample(dat.kasdin.cleaned$Closer_vals, size=n, replace=T)
 cts[i] <- (mean(curr.sample) - mu0)/(cs/sqrt(n))
 } 

 p2 <- ggplot() +
   stat_density(data=tibble(t=cts), aes(x=t), color="grey", geom="line")+
   geom_hline(yintercept=0) +
   theme_bw()+
   labs(x=bquote(t),
   y="Density",
   caption=paste("mean:", round(mean(cts),2), ", sd:", round(sd(cs),2)))+
   ggtitle("Closer Values") # Plot title

 # Resampling
 dts <- rep(NA, 1000)
 ds <- sd(dat.kasdin.cleaned$difference)
 n <- nrow(dat.kasdin.cleaned)
 for(i in 1:1000){
 curr.sample <- sample(dat.kasdin.cleaned$difference, size=n, replace=T)
 dts[i] <- (mean(curr.sample) - mu0)/(ds/sqrt(n))
 } 

 p3 <- ggplot() +
   stat_density(data=tibble(t=dts), aes(x=t), color="grey", geom="line")+
   geom_hline(yintercept=0) +
   theme_bw()+
   labs(x=bquote(t),
   y="Density",
   caption=paste("mean:", round(mean(dts),2), ", sd:", round(sd(ds),2)))+
   ggtitle("Differences") # Plot title

(p1 | p2 | p3)
```

```{r}
closer.sampling.summary = tibble(t=cts) |>
  summarize( #calculates data for a table with the following measures
    Skewness = e1071::skewness(cts, na.rm = T),
    "Excess Kurtosis" = e1071::kurtosis(cts, na.rm = T)
  ) 
```

```{r}
farther.sampling.summary = tibble(t=cts) |>
  summarize( #calculates data for a table with the following measures
    Skewness = e1071::skewness(fts, na.rm = T),
    "Excess Kurtosis" = e1071::kurtosis(fts, na.rm = T)
  ) 
```

```{r}
#| label: tbl-sampling-dist-farther
#| tbl-cap: "Sampling Distributions for Farther Values"
#| tbl-align: "center"
#| echo: false
farther.sampling.summary |>
  knitr::kable(digits = 3) #digits specify decimal in table values
```

```{r}
#| label: tbl-sampling-dist-closer
#| tbl-cap: "Sampling Distributions for Closer Values"
#| tbl-align: "center"
#| echo: false
closer.sampling.summary |>
  knitr::kable(digits = 3) #digits specify decimal in table values
```

```{r}
difference.sampling.summary = tibble(t=dts) |>
  summarize( #calculates data for a table with the following measures
    Skewness = e1071::skewness(dts, na.rm = T),
    "Excess Kurtosis" = e1071::kurtosis(dts, na.rm = T)
  ) 
```

```{r}
#| label: tbl-sampling-dist-differences
#| tbl-cap: "Sampling Distribution for Difference"
#| tbl-align: "center"
#| echo: false
difference.sampling.summary |>
  knitr::kable(digits = 3) #digits specify decimal in table values
```

* The sample is generalizable to the adult zebra finch population in Area X.
* Researchers collected the observations through randomization, so observations are independent.
* The sampling distributions are all approximately normal with minimal skew and excess kurtosis, so our sampling distribtution assumptions are met.



* "The close responses differed significantly from 0 ($p=1.63 \times 10^{-8}$).''\
**Note**: Use the appropriate one-sided test.


```{r}
hedges_g(x=dat.kasdin.cleaned$Closer_vals, mu = 0, alternative = "greater")
t.test(x=dat.kasdin.cleaned$Closer_vals, mu=0, alternative="greater")
```

We have discernable support that the zebra finches in Area X had increased dopamine levels while singing closer. ($t=9.1573$, $p= 1.333 \times 10^{-9}$; $g=1.77$; 95% CI: $0.1452511$, $\infty$)

* "The far responses differed significantly from 0 ($p=5.17 \times 10^{-8}$).''\
**Note**: Use the appropriate one-sided test.

```{r}
hedges_g(x=dat.kasdin.cleaned$Farther_vals, mu = 0, alternative = "less")
t.test(x=dat.kasdin.cleaned$Farther_vals, mu=0, alternative="less")
```

We have discernable support that the zebra finches in Area X had decreased dopamine levels while singing farther away.($t=-7.9245$, $p= 1.866 \times 10^{-8}$; $g=-1.54$; 95% CI: $-\infty$, $4.60$)

* "The difference between populations was significant ($p=1.04 \times10^{-8}$).''\
**Note**: Use the two-sided test.

```{r}
hedges_g(x=dat.kasdin.cleaned$difference, mu = 0, alternative = "two.sided")
t.test(x=dat.kasdin.cleaned$difference, mu=0, alternative="two.sided")
```

We have discernable support that the zebra finches in Area X had different dopamine levels depending on their distance.($t=9.1428$, $p= 0.746 \times 10^{-9}$; $g=1.77$; 95% CI: $0.303$, $0.480$)

## Part e 

For each hypothesis test in the previous question, plot the null $T$ 
distribution and the observed $t$ statistic. Ensure to use \texttt{geom\_ribbon()} 
to highlight the rejection region and the $p$-value. Additionally, add the 
resampling distribution for $T$ to the chart to demonstrate any differences 
between the null distribution and the distribution suggested by the data.


```{r}
#| label: fig-Farther-HPtest
#| fig-cap: "T test distributions for Farther Values."
#| fig-width: 10
#| fig-height: 6
#| scale: "80%"
#| fig-align: "center"

mu0 = 0

t.stat = t.test(x=dat.kasdin.cleaned$Farther_vals, 
                mu=0, 
                alternative="less")$statistic
  # gives t statistic of data

t.critical = qt(1-0.05, df=24)
#gives critical t value

ggdat <- tibble(t = seq(-4, 4, length.out=1000)) |>
 mutate(pdf.h0 = dt(t, df=24))


 # create vector of axis ticks
 t.breaks <- seq(-24, 24, 4)
 xbar.breaks <- round(t.breaks * (fs/sqrt(n)) + mu0, 2)

 ggplot(ggdat) +
 geom_line(aes(x=t, y=pdf.h0, color="Null"))+ # plot distribution of T under H0
 stat_density(data=tibble(t=fts), #plot distribution of T under HA
          aes(x=t, color= "Alternative"), 
          geom="line")+
 geom_hline(yintercept=0) +
 geom_ribbon(data = ggdat|> filter(t <= -t.critical), #fills area after t= 0.95
  aes(x=t, ymin=0, ymax= pdf.h0), #max keeps it from going above line
  fill= "darkorchid2", alpha= .5) +
geom_ribbon(data = ggdat|> filter(t >= t.critical), #fills area after t= 0.95
  aes(x=t, ymin=0, ymax= pdf.h0), #max keeps it from going above line
  fill= "darkorchid2", alpha= .5) +
 # Plot observation
 geom_point(data=tibble(x=t.stat, y=0),
 aes(x=x, y=y), color="red", size=3) +
 
# Plot mirrored observation
 geom_point(data=tibble(x=-t.stat, y=0),
 aes(x=x, y=y), color="red", size=3, alpha=0.3) +
 theme_bw()+
 # Specify axis ticks
 scale_x_continuous("t", breaks=t.breaks,
 sec.axis = sec_axis(~., bquote(bar(x)),
breaks=t.breaks,
labels=xbar.breaks))
```

```{r}
#| label: fig-Closer-HPtest
#| fig-cap: "T test distributions for Closer Values."
#| fig-width: 10
#| fig-height: 6
#| scale: "80%"
#| fig-align: "center"

mu0 = 0

t.stat = t.test(x=dat.kasdin.cleaned$Closer_vals, 
                mu=0, 
                alternative="less")$statistic

ggdat <- tibble(t = seq(-4, 4, length.out=1000)) |>
 mutate(pdf.h0 = dt(t, df=24))

 # create vector of axis ticks
 t.breaks <- seq(-24, 24, 4)
 xbar.breaks <- round(t.breaks * (cs/sqrt(n)) + mu0, 2)

 ggplot(ggdat) +
 geom_line(aes(x=t, y=pdf.h0, color="Null"))+ # plot distribution of T under H0
 stat_density(data=tibble(t=cts), #plot distribution of T under HA
          aes(x=t, color= "Alternative"), 
          geom="line")+
 geom_hline(yintercept=0) +
 geom_ribbon(data = ggdat|> filter(t <= -t.critical), #fills area after t= 0.95
  aes(x=t, ymin=0, ymax= pdf.h0), #max keeps it from going above line
  fill= "darkorchid2", alpha= .5) +
geom_ribbon(data = ggdat|> filter(t >= t.critical), #fills area after t= 0.95
  aes(x=t, ymin=0, ymax= pdf.h0), #max keeps it from going above line
  fill= "darkorchid2", alpha= .5) +
 # Plot observation
 geom_point(data=tibble(x=t.stat, y=0),
 aes(x=x, y=y), color="red", size=3) +
 # Plot mirrored observation

 geom_point(data=tibble(x=-t.stat, y=0),
 aes(x=x, y=y), color="red", size=3, alpha=0.3) +
 theme_bw()+
 # Specify axis ticks
 scale_x_continuous("t", breaks=t.breaks,
 sec.axis = sec_axis(~., bquote(bar(x)),
breaks=t.breaks,
labels=xbar.breaks))
```

```{r}
#| label: fig-Differences-HPtest
#| fig-cap: "T test distributions for Differences in Values."
#| fig-width: 10
#| fig-height: 6
#| scale: "80%"
#| fig-align: "center"

mu0 = 0

t.stat = t.test(x=dat.kasdin.cleaned$difference, 
                mu=0, 
                alternative="two.sided")$statistic

ggdat <- tibble(t = seq(-4, 4, length.out=1000)) |>
 mutate(pdf.h0 = dt(t, df=24))

 # create vector of axis ticks
 t.breaks <- seq(-24, 24, 4)
 xbar.breaks <- round(t.breaks * (ds/sqrt(n)) + mu0, 2)

 ggplot(ggdat) +
 geom_line(aes(x=t, y=pdf.h0, color="Null"))+ # plot distribution of T under H0
 stat_density(data=tibble(t=dts), #plot distribution of T under HA
          aes(x=t, color= "Alternative"), 
          geom="line")+
 geom_hline(yintercept=0) +
 geom_ribbon(data = ggdat|> filter(t <= -t.critical), #fills area after t= 0.95
  aes(x=t, ymin=0, ymax= pdf.h0), #max keeps it from going above line
  fill= "darkorchid2", alpha= .5) +
geom_ribbon(data = ggdat|> filter(t >= t.critical), #fills area after t= 0.95
  aes(x=t, ymin=0, ymax= pdf.h0), #max keeps it from going above line
  fill= "darkorchid2", alpha= .5) +
 # Plot observation
 geom_point(data=tibble(x=t.stat, y=0),
 aes(x=x, y=y), color="red", size=3) +
 # Plot mirrored observation

 geom_point(data=tibble(x=-t.stat, y=0),
 aes(x=x, y=y), color="red", size=3, alpha=0.3) +
 theme_bw()+
 # Specify axis ticks
 scale_x_continuous("t", breaks=t.breaks,
 sec.axis = sec_axis(~., bquote(bar(x)),
breaks=t.breaks,
labels=xbar.breaks))
```

## Citations

I used R [@R] for my coding language, the knitr package [@knitr] for organizing graphs, the patchwork package [@patchwork] to make clean graphs, and the tidyverse package [@tidyverse] for more readable code and graphs. I used the e1071 package for excess kurtosis calculations [@e1071]; I used the effect size package [@effectsize] to calculate the effect sizes; I used the pwr package [@pwr] for power calculations.